Merging Datasets Through Deep learning

### 2018-09-04 paper2018/evaluation.tex
conclusions

\subsection{Conclusion and Future Work}
We have described techniques that are useful to build deep learning models that can be used effectively for joins, and we will provide these models to the community for use.  Being able to build generic models that can be used for merging datasets seems to be a plausible idea, with caveats in terms of how one builds these models.

%Our results and our comparison with faces seems to show that training on hard negatives does not compromise recall overall and can boost precision for near neighbors.  Since joins will be most effective and efficient by focusing on a small, precise neighborhood, training on hard negatives may in fact be a useful addition.

>>>>

\section{Conclusion and Future Work}
We show that deep learning models can be used effectively for joins, and we will provide these models to the community for use.  In the future, we will evaluate our work on other entity types and continue to explore refinements of both loss functions and triplet selection.
